---
title: "hw01_YongzhengParkerLi.Rmd"
output: html_document
---

This file is for the first assignment of the course STAT545A. It aims to explore a dataset via using R Markdown.

## Setting Up

```{r 01}
install.packages("cem",repos = "http://cran.us.r-project.org")
library(cem)
data(LL)
data <- LL
colnames(data)
```

This part shows the package and dataset installation process. It also gives the variable names.

## Basic Data Frame Exploration

```{r 02}
re74.bar <- mean(LL$re74)
re74.bar
median(LL$re74)
summary(LL$re74)
summary(LL)
table(LL$black)
which.max(table(LL$education))
table(LL$education)
freq.education <- table(LL$education)
which.max(freq.education)
prop.table(table(LL$education))
prop.table(table(LL$education))*100
```

This section explores the mean and median of one variable within a dataframe. Furthermore, it summaries statistics of all variables within a dataframe and gives different styles of count/frenquency tables.

# Measures of Dispersion

```{r 03}
var(LL$re74)
sd(LL$re74)
install.packages("moments",repos = "http://cran.us.r-project.org")
library(moments)
skewness(LL$re74)
kurtosis(LL$re74)
sd.re74 <- sqrt(var(LL$re74))
sd.re74
```

This section measuares dispersion: variance, standard deviation, skewness, and kurtosis.

# T-test

```{r 04}
t.test(LL$re74, mu=6059, alternative="less")
t.test(re78 ~ treated, data=LL, alternative = "less", var.equal=FALSE)
LL.0 <- subset(LL, treated==0)
t.test(LL.0$re74, LL.0$re78, alternative = "less", paired = TRUE)
LL.1 <- subset(LL, treated==1)
t.test(LL.1$re74, LL.1$re78, alternative = "less", paired = TRUE)
```

This chunk does the one-sample t-test and two-sample t-test (both independet samples and dependet samples).

# Cross-Tabulations and Correlation

```{r 05}
install.packages("gmodels",repos = "http://cran.us.r-project.org")
library(gmodels)
CrossTable(y=LL$u75, x=LL$treated)
CrossTable(y=LL$u75, x=LL$treated, prop.c=TRUE,
prop.r=FALSE, prop.t= FALSE, prop.chisq=FALSE, chisq=TRUE,
format="SPSS")
cor(LL$education, LL$re74)
```

The final section gives a further data exploration of cross-tabluation and correlation.
